\documentclass[msci]{abdnthesis}
%TC:ignore
\usepackage{color,soul}
\usepackage[numbers]{natbib}
\usepackage[utf8]{inputenc}
\usepackage{subfig}
\usepackage[nopostdot]{glossaries}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{listings}
\lstset{basicstyle=\ttfamily,
  frame=single,
  showstringspaces=false,
  commentstyle=\color{black},
  keywordstyle=\color{black}
}
\setlength{\bibsep}{0pt}
\bibliographystyle{apalike}
\graphicspath{ {./img/} }

\usepackage[edges]{forest}

\definecolor{foldercolor}{RGB}{124,166,198}

\tikzset{pics/folder/.style={code={%
    \node[inner sep=0pt, minimum size=#1](-foldericon){};
    \node[folder style, inner sep=0pt, minimum width=0.3*#1, minimum height=0.6*#1, above right, xshift=0.05*#1] at (-foldericon.west){};
    \node[folder style, inner sep=0pt, minimum size=#1] at (-foldericon.center){};}
    },
    pics/folder/.default={20pt},
    folder style/.style={draw=foldercolor!80!black,top color=foldercolor!40,bottom color=foldercolor}
}

\forestset{is file/.style={edge path'/.expanded={%
        ([xshift=\forestregister{folder indent}]!u.parent anchor) |- (.child anchor)},
        inner sep=1pt},
    this folder size/.style={edge path'/.expanded={%
        ([xshift=\forestregister{folder indent}]!u.parent anchor) |- (.child anchor) pic[solid]{folder=#1}}, inner xsep=0.6*#1},
    folder tree indent/.style={before computing xy={l=#1}},
    folder icons/.style={folder, this folder size=#1, folder tree indent=3*#1},
    folder icons/.default={12pt},
}

\usepackage[T1]{fontenc}
\usepackage{color,soul}
\usepackage{enumitem}
\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}
\renewcommand{\arraystretch}{1.5}
\title{%
FlyTrap \\
\large\ \\
\huge Decentralised Blockchain Authorization \& Auditing Architecture for IoT and MQTT Brokers}
\author{Konrad M. Dryja}
\school{Department of Computing Science}

%%%% In the final submission of a thesis, this should only be the year
%%%% of submission.  However, it is useful to use \date{\today} for drafts so that
%%%% they don't get mixed up.
    
\date{2020}

%% It is useful to split the document up as chapters and include
%% them.  LaTeX will sort out all the numbering and cross-referencing
%% for you --- if you run it enough times!

%% If you want to include only a couple of chapters then use the
%% \includeonly{} command with a list of the file/chapter names that
%% you wish to include.  NB, this must be in the preamble.

% \includeonly{introduction,faq}

\def\sfthing#1#2{\def#1{\mbox{{\small\normalfont\sffamily #2}}}}

\sfthing{\PP}{P}
\sfthing{\FF}{F}

%% This will make sure that all cross-references are correct (including
%% references to those file not included) but will produce a dvi
%% file with only those files/chapters you specify included.

\makenoidxglossaries
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{abi}{ABI}{Application Binary Interface}
\newacronym{json}{JSON}{Javascript Object Notation}
\newacronym{eth}{ETH}{Ethereum}
\newacronym{evm}{EVM}{Ethereum Virtual Machine}
\newacronym{btc}{BTC}{Bitcoin}
\newacronym{mqtt}{MQTT}{Message Queuing Telemetry Transport}
\newacronym{gdpr}{GDPR}{General Data Protection Regulation}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{tcp}{TCP}{Transmission Control Protocol}
\newacronym{ACL}{ACL}{Access Control List}
\newacronym{CCPA}{CCPA}{California Consumer Privacy Act}
\newacronym{TLS}{TLS}{Transport Layer Security}
\newacronym{PII}{PII}{Personal Identifiable Information}
\newacronym{QOS}{QoS}{Quality of Service}
\newacronym{POW}{PoW}{Proof-of-Work}
\newacronym{POS}{PoS}{Proof-of-Stake}
\newacronym{POA}{PoA}{Proof-of-Authority}
\newacronym{DPA}{DPA}{Data Protection Act}
\newacronym{CLI}{CLI}{Command Line Interface}
\newacronym{API}{API}{Application Programming Interface}
\newacronym{ECDSA}{ECDSA}{Elliptic Curve Digital Signature Algorithm}
\glsaddall

\begin{document}

%%%% Create the title page and standard declaration.

\maketitle
\makedeclaration

%%%% Then the abstract and acknowledgements

\begin{abstract}
  In this paper I present a novel approach introducing Authentication, Authorization and Accountability to MQTT Brokers. 
\end{abstract}

\begin{acknowledgements}
  First and foremost, I would like to thank Prof Peter Edwards and Dr Milan Markovic for their incredible help supervising my project. They were always happy to answer my questions and always found time to accommodate any additional requests. I could always count on their accurate and critical feedback. I could not have imagined to have anyone better guide me in this final year of my University adventure.

  I would also like to acknowledge Computing Science class 2019, which I was part of until the very end (before departing on my placement) along with class 2020. The countless days spent on studying for Robotics, Algorithmic Problem Solving or Security.

  To my parents who sacrificed a lot to give me the future I am living in right now. I am beyond grateful and probably will never be able to repay.

  My entire team from Google Zurich: Caroline Muthambiri, Joe Coyne, Patrick Oberholzer - and especially Edu Campillo - where I was working during my industrial placement. You made me feel like part of the bigger effort and you inspired me to keep pushing beyond my limits. If it wasn't for you, I'd still be stuck trying to make Python2.7 happen, instead of moving forward. I look forward to working alongside you.

  Dr Liana Marinescu for being an incredible help, always supportive regardless of circumstances and always ready to sacrifice the day to cheer others up. I don't think I would be able to push through my conversion and my final year of University without you. You're a treasure.

  Last but not least, Mikko. For the late-night tech discussions. For the takeaways in Meston. For countless failed projects. For struggling through our internships. I bid you farewell as my University colleague and will welcome you very soon as a coworker.

 And to everyone else I forgot to mention, but were part of my journey - thank you! 

  
\end{acknowledgements}


%%%% It should have a table of contents, but delete the other two as
%%%% necessary.

\tableofcontents\vfill Word count: 17382
% \listoftables
% \listoffigures

\printnoidxglossary[type=\acronymtype,title=Abbreviations,nonumberlist]
% \printglossary[type=\acronymtype,style=long,nonumberlist]

%TC: endignore
\include{introduction}
\include{background}
\include{requirements}
\include{design}
\include{implementation}
\include{evaluation}
\include{discussion}

%TC:ignore
\appendix
\include{manual}
\include{maintenance}

\bibliography{mybib}
%TC:endignore
\end{document}
